---
title: "Assignment-2 Submission for CIS 8392"
author: "Narendra Bandi"
date: "01/04/2021"
output: html_document
---
<style>
table {
  margin: auto;
  border-top: 1px solid #666;
  border-bottom: 1px solid #666;

}
table thead th { border-bottom: 1px solid #ddd; }
th, td { padding: 5px; }
thead, tfoot, tr:nth-child(even) { background: #eee; }
</style>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r echo=TRUE, message=FALSE}
library(httr)
library(gh)
library(tidyverse)
 
```

#### Describe the GitHub user and provide the URL to the GitHub page of the user 

WIX Engineering develops Technologies for cloud and web application development, and they opensource the source codde.
WIX GitHub group URL is [https://github.com/wix]

#### (2) Table showing the user's id, name, public_repos, followers
```{r echo=FALSE}
my_token = "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"
Sys.setenv(GITHUB_TOKEN = my_token)
```

```{r echo = TRUE}
## Get groups's id, name, public_repos, followers
wix_git <- gh("/orgs/wix",.limit = Inf, .token =  my_token)
wix_id <-  wix_git[["id"]]
wix_name <- wix_git[["name"]]
wix_public_repo_count <- wix_git[["public_repos"]]
wix_members <- gh("/orgs/wix/members", .limit = Inf,.token =  my_token) 
wix_members_count <- length(wix_members)
wix_followers_count <- wix_git[["followers"]]
wix_table <- (c("Id" =  wix_id, "Name" = wix_name, 
                 "Public Repos" = wix_public_repo_count, "Members" = wix_members_count))


```

WIX Group details:

```{r echo=TRUE, message = F}
knitr::kable(wix_table, col.names = "", format = "html", align = "c")
```


##### (3) A table summarizing the followers' id, name, public_repos, followers

```{r echo=TRUE, message=F}
## Function to get  Group Member details
members_details_func <- function(x)
{
   tryCatch(
    {
      member_data <- gh(x[["url"]],.token = my_token, .limit = Inf)
      id <- member_data["id"]
      name <- member_data["name"]
      public_repos <- member_data["public_repos"]
      followers <- member_data[ "followers"]
      return(list("Id" = id, "Name" = name, "Public Repos" = public_repos, "Followers" = followers))
    },
    error =  function(err) {
      return(list("Id" = NA, "Name" = NA, "Public Repos" = NA, "Followers" = NA))
    }
  ) }

members.df <- map_df(wix_members, members_details_func)
members.count <- nrow(members.df)
```


The "WIX" Git group has `r members.count` members, Below table shows the details of frist 20 Members:


```{r echo= TRUE, message=F}
knitr::kable(head(members.df, 20) , format = "html", align = "c" )

```

##### (4) A table summarizing the repositories'
##### name, language, size, forks_count, stargazers_count, watchers_count, open_issues_count

```{r echo= TRUE, message=F}
wix_repos <- gh("GET /orgs/wix/repos", .limit = Inf, .token =  my_token)
```

```{r echo = TRUE, message=F}
## Function to get REPO details
get_repo_details<- function(x) {
tryCatch(
  {
    name <- x["name"]
    language <- x["language"]
    size <- x["size"]
    forks_count <- x["forks_count"]
    stargazers_count <- x["stargazers_count"]
    watchers_count <- x["watchers_count"]
    open_issues_count <- x["open_issues_count"]
    
    return(list("Name" = name, "Language" = language,
                "Forks Count" = forks_count,"Stargazers Count" = stargazers_count,
                "Watchers Count" = watchers_count ,"Open Issues Count" = open_issues_count))
  },
  error =  function(err) {
    return(c(
      "Name" = NA,  "Language" = NA,"Forks Count" = NA,
      "Stargazers Count"= NA, "Watchers Count" <- NA,  "Open Issues Count" <- NA
    ))})}

repos.detials.df <- map_df(wix_repos, get_repo_details)
```

The WIX group on Git hub has `r nrow(repos.detials.df)` repos, Below table shows the details of first 20 repos.

```{r echo= TRUE,message=FALSE}
knitr::kable(head(repos.detials.df, 20), align = "c",format = "html")
```

##### (5) A table summarizing the issues. The table should include the following
##### columns: repo name, the number of open issues in the repo, the number of
##### closed issues in the repo, the average duration to close an issue in the repo

Below code retrieves the number of Open and Closed issues for each repository, using the 
R "datediff" function, duration between closing and creation of an issue is calculated, "Minutes" is used as the unit for calculting difference..

The calcuated duration is convreted into Days.


```{r echo= TRUE,message = F}


get_issue_details <- function(repo)
{
  tryCatch(
  {
  repo_name <-  repo[["name"]]
  repo_full_name <- repo[["full_name"]]
  issue_url = paste0("https://api.github.com/repos","/",repo_full_name,"/", "issues")
  
  closed_issues <-  gh(issue_url,state= "closed", .limit = 50, .token = my_token )
  
  open_issue_count <- repo[["open_issues_count"]]
  closed_issues_count <- length(closed_issues)
  duraton_to_fix_minutes <- 0
  
  if (closed_issues_count > 0) {
    duraton_to_fix_minutes <- map_dbl(closed_issues, function(X)
    {
      duration_minutes <- difftime(X$closed_at, 
                                   X$created_at, units = "mins")
      duration_minutes
    })}
  
    avg_duration_minutes <- mean(duraton_to_fix_minutes, na.rm = TRUE)
    avg_duration_days <- round(avg_duration_minutes/(60*24), 1)
  
  issue_list<- list("Name" = repo_name,
                    "Open" = open_issue_count, 
                    "Closed" = closed_issues_count,
                    "Avg Duration (Days)" = avg_duration_days )
  
  
  return (issue_list)
  },
  error =  function(err) {
    return (issue_list<- c("Name" = NA,
                              "Open" = NA, 
                              "Closed" = NA,
                              "Avg Duration (Days)" = NA ))
  })
}
 
open_close_issue_df <- map_df(wix_repos[1:25], get_issue_details)

```
 Below table shows the details of Number of  open and close issues, Duration to fix for first 20 repos.

```{r echo= TRUE,message=FALSE}
knitr::kable( head(open_close_issue_df, 20), align = "c", format = "html")
```


#####  Plots
```{r echo= FALSE}
vect_func <- function(x)
{
  vect <- c()
  for (variable in x) 
  {
    if (is.null(variable[[1]]))
    {
      vect <- append(vect, NA)
    }
    else
    {
      vect <- append(vect, variable[[1]])
   }}
  
  return (vect)
  
repos.detials.df$Language <- vec_func(repos.detials.df$Language)
repos.detials.df$`Forks count` <- vec_func(repos.detials.df$`Forks count`)
repos.detials.df$`Stargazers Count` <- vec_func(repos.detials.df$`Stargazers Count` )
repos.detials.df$`Watchers Count` <- vec_func(repos.detials.df$`Watchers Count`)
repos.detials.df$`Open Issues Count` <- vec_func(repos.detials.df$`Open Issues Count`)
repos.detials.sub.df <- repos.detials.df %>% select(-"Name")
}
```



